---
title: "Study One: Confirmatory Tests"
author: "Joel Larwood"
date: "2019-09-23"
output: workflowr::wflow_html
---

## Introduction


## A note: This data was submitted for peer review, the manuscript submitted can be seen here: . The paper was withdrawn from review pending the collection of new data (studies two and three). The hypotheses have been retained. There was no pre-registration for this study 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(apa)
library(apaTables)
library(visdat)
library(emmeans)
library(sjPlot)
library(sjmisc)
library(skimr)
library(psych)
library(multcomp)
library(ggridges)
```

```{r loadS1, message=FALSE, warning = FALSE}
s1raw <- read_csv("data/s1.csv") 

names(s1raw)
```


```{r scores}
s1dat <- s1raw %>% 
  mutate(Baseline = rowSums(dplyr::select(., POMSDSF1_1:POMSDSF8_1)),
         PostInduction = rowSums(dplyr::select(., POMSDSF1_2:POMSDSF8_2)),
         PostListening = rowSums(dplyr::select(., POMSDSF1_3:POMSDSF8_3)),
         MARS_Pos = rowMeans(dplyr::select(., MARS1_1,
                                           MARS2_1,
                                           MARS6_1,
                                           MARS7_1, 
                                           MARS8_1,
                                           MARS9_1,
                                           MARS11_1,
                                           MARS12_1,
                                           MARS14_1,
                                           MARS15_1)),
         MARS_Neg = rowMeans(dplyr::select(., MARS3_1,
                                           MARS4_1,
                                           MARS5_1,
                                           MARS10_1,
                                           MARS13_1)),
         RRQ6_1 = 6 - .$RRQ6_1,
         RRQ9_1 = 6 - .$RRQ9_1,
         RRQ10_1 = 6 - .$RRQ10_1, 
         Condition = as.factor(Condition),
         Condition = fct_recode(Condition, 
                                "Control" = "1", 
                                "Self Selected" = "2",
                                "Experimeter Selected" = "3"))
s1dat <- s1dat %>% 
  mutate(
    Rumination = rowMeans(dplyr::select(., RRQ1_1:RRQ12_1)),
    RumSplit = as.factor(if_else(Rumination < median(Rumination),
                                 "Low Rumination",
                                 "High Rumination"))
  )



s1dat %>% 
  dplyr::select(Baseline, PostInduction, PostListening, Rumination, MARS_Pos, MARS_Neg) %>%
  skimr::skim() %>% 
  skimr::kable()

table(s1dat$RumSplit)

write_csv(s1dat, "data/s1Processed.csv")

```

# Reliabilities 
```{r alphas}
# Baseline ALpha 
psych::alpha(dplyr::select(s1dat, POMSDSF1_1:POMSDSF8_1 ))$total$raw_alpha

# Post Induction Alpha
psych::alpha(dplyr::select(s1dat, POMSDSF1_2:POMSDSF8_2 ))$total$raw_alpha

# Post Listening Alpha 
psych::alpha(dplyr::select(s1dat, POMSDSF1_3:POMSDSF8_3 ))$total$raw_alpha

# Rumination Alpha 
psych::alpha(dplyr::select(s1dat, RRQ1_1:RRQ12_1 ))$total$raw_alpha

# MARS Positive Alpha 
psych::alpha(dplyr::select(s1dat, MARS1_1,
                           MARS2_1,
                           MARS6_1,
                           MARS7_1, 
                           MARS8_1,
                           MARS9_1,
                           MARS11_1,
                           MARS12_1,
                           MARS14_1,
                           MARS15_1))$total$raw_alpha


#MARS Negative Alpha 
psych::alpha(dplyr::select(s1dat, MARS3_1,
                           MARS4_1,
                           MARS5_1,
                           MARS10_1,
                           MARS13_1))$total$raw_alpha

```

## ANOVA 
Here, we can see that there is a signifciant main efffect of timepoint and rumination group but not condition. There is also a significant timepoint*condition interaction 
```{r ANOVAs1}

s1long <- gather (
  s1dat,
  key = Timepoint,
  value = Sadness,
  Baseline, PostInduction, PostListening
) 



ANOVAs1 <- afex::aov_car(
  formula = Sadness ~ Timepoint*Condition*RumSplit + Error(id/Timepoint),
  data = s1long,
  type = 2,
)

anova_apa(ANOVAs1, 
          es = "ges"
)

```

The main effect of time is charactersied by an increase from time 1 to time two and a decrease from time 2 to time 3
```{r ANOVAs1TimeMainEffect}
# summary(as.glht(pairs(m1)), test=adjusted("free")) code for adjusted pvalues
maineffecttime <- emmeans(ANOVAs1, ~Timepoint)

summary(as.glht(pairs(maineffecttime), test=adjusted("free")))
```

We can also see that over all TImepoints and conditions people high in rumination have higher sadness scores 
```{r ANOVAs1RumSplitMainEffect}

maineffectrum <- emmeans(ANOVAs1, ~ RumSplit)

summary(as.glht(pairs(maineffectrum)), test = adjusted("free"))


afex::afex_plot(ANOVAs1,
                x = "RumSplit",
                data_plot = TRUE,
                error = "between",
                plot_plot = TRUE,
                error_ci = TRUE)+
  ggplot2::theme_classic()
```


Following up the interaction we can see that it is qualified by each group returning to baseline levels of sadness excepted for the sad music group
```{r ANOVAs1interaction}
timepointsimpleeffect <- emmeans(ANOVAs1, ~ Timepoint|Condition)

summary(as.glht(pairs(timepointsimpleeffect)), test = adjusted("free"))

conditionsimpleeffect<- (emmeans(ANOVAs1, ~ Condition|Timepoint))

summary(as.glht(pairs(conditionsimpleeffect)))
```

```{r ANOVAs1plot}
afex::afex_plot(ANOVAs1,
x = "Timepoint",
trace = "Condition", 
mapping = "color",
data_plot = FALSE) +
ggplot2::theme_classic() + 
ggplot2::scale_x_discrete(labels = c("Baselie", "Post Induction", "Post Listening")) +
ggplot2::ylim(0, 15) +
ggplot2::theme(legend.title = element_blank())

```


```{r RumCor}
s1dat %>% 
dplyr::select("Rumination", "MARS_Neg", "MARS_Pos") %>% 
apaTables::apa.cor.table(filename = "docs/s1MARScor.txt",
landscape = FALSE)
```
