---
title: "Study One: Exploratorty Data Analysis (Timepoints)"
author: "Joel Larwood"
date: "2019-09-23"
output:
  workflowr::wflow_html:
    code_folding: hide
editor_options:
  chunk_output_type: console
---

# An exploratory saturdated model
```{r echo = FALSE}
knitr::opts_chunk$set(autodep = TRUE, message = FALSE, warnings = FALSE)
```


In the dataset we also collected data about the BRECVEMA mechanism occuring during listening, demogrpahics and how likely they were to use the song for regulation. 

```{r loads1data, message = FALSE}
library(tidyverse)
s1longExplore <- read_csv("data/s1long.csv") %>% 
  dplyr::select(id, 
                Sadness,
                Timepoint, 
                rumination, 
                Baseline,
                age,
                gender, 
                contains("mec"), 
                musebaq, 
                reg.use_1, 
                valence, 
                energy) %>% 
  drop_na()  %>% 
   mutate_at(.vars = vars(mecscale_1:mecscale_8), 
              factor) %>% 
   mutate_at(.vars = vars (mecscale_1:mecscale_8),
             .funs = forcats::fct_recode, 
             "No" = "2", 
             "Yes" = "1") %>% 
    dplyr::rename(brainstem = mecscale_1,
                        Entrainment = mecscale_2,
                        Memory = mecscale_3, 
                        Conditioning = mecscale_4,
                        Imagery = mecscale_5, 
                        Contagion = mecscale_6, 
                        Expectancy = mecscale_7,
                        Appraisal = mecscale_8)
```

So I want to build some models with control mechanisms coming in at each point 

## Model 1 is the timepoint only model 
```{r timepointonly, message=FALSE}
library(sjPlot)
timepoint <- lmerTest::lmer(Sadness~1 + Timepoint + (1 |id), data = s1longExplore)
tab_model(timepoint)

```

## Model 2 I add demographics 

```{r message=FALSE}
demo <- lmerTest::lmer(Sadness~1 + Timepoint + age + gender + (1 |id), data = s1longExplore)
tab_model(demo)
```

## Model 3 I add spotify data 
 
```{r message=FALSE}
spotifyvar <- lmerTest::lmer(Sadness~1 + Timepoint + age + gender + valence + energy +  (1 |id), data = s1longExplore)
tab_model(spotifyvar)
```

## Model 4 I add the BRECVEMA mechanisms 

```{r message=FALSE}
mecscale <- lmerTest::lmer(Sadness~1 + Timepoint + age + gender + valence + energy + brainstem + Entrainment + Memory + Conditioning + Imagery + Contagion + Expectancy + Appraisal + (1 |id), data = s1longExplore)

tab_model(mecscale)
```

## Model 5 I add how likely they are to listen to the song when they are sad  

```{r message=FALSE}
likelyuse <- lmerTest::lmer(Sadness~1 + Timepoint + age + gender + valence + energy + brainstem + Entrainment + Memory + Conditioning + Imagery + Contagion + Expectancy + Appraisal + reg.use_1 + (1 |id), data = s1longExplore)

tab_model (likelyuse)
```

## Model 6 I add the MUSEBAQ 

```{r message=FALSE}
musebaqglmm <- lmerTest::lmer(Sadness~1 + Timepoint + age + gender + valence + energy + brainstem + Entrainment + Memory + Conditioning + Imagery + Contagion + Expectancy + Appraisal+ reg.use_1 + musebaq + (1 |id), data = s1longExplore)

tab_model(musebaqglmm)
```

## Model 7 I add rumiation 

```{r message=FALSE}
ruminationmain <- lmerTest::lmer(Sadness~1 + Timepoint + age + gender + valence + energy + brainstem + Entrainment + Memory + Conditioning + Imagery + Contagion + Expectancy + Appraisal+ reg.use_1 + musebaq + rumination +  (1 |id), data = s1longExplore)

tab_model(ruminationmain)
```

## Finally I add the interaction term 
```{r message=FALSE}
ruminationint <- lmerTest::lmer(Sadness~1 + Timepoint + age + gender + valence + energy + brainstem + Entrainment + Memory + Conditioning + Imagery + Contagion + Expectancy + Appraisal + reg.use_1 + musebaq +rumination + rumination:Timepoint + (1 |id), data = s1longExplore)

tab_model(ruminationint)
```

# Model comparisons 
Now I want to compare these models 
```{r message=FALSE}
knitr::kable(anova(timepoint, demo, spotifyvar, mecscale, likelyuse, musebaqglmm, ruminationmain, ruminationint))
```

# Automatic Model 

Now I am going to do an exploratory analysis to find the best fitting model

```{r message = FALSE, results = "hide", cache = TRUE}
library(buildmer)
saturatedformula <- Sadness~1 + Timepoint + age + gender + valence + energy + brainstem + Entrainment + Memory + Conditioning + Imagery + Contagion + Expectancy + Appraisal + reg.use_1 + musebaq +rumination + rumination:Timepoint + (1 |id)

buildmer::buildmer(formula = saturatedformula, data = s1longExplore, crit = "AIC")

```


the best model was identifed as containing </br>
- rumination </br>
- Timepoint </br>
- The interaction of rumination and timepoint </br>
- The likehood of the song being used for emotion regulation </br>
- Brainstem reflex </br>
- Aprraisal </br>
- Trat use of music for emotional and cognitive regulation


## The model results are 
```{r, message=FALSE}

selected <- lmerTest::lmer(Sadness ~ 1 + rumination + reg.use_1 + brainstem + Appraisal + Timepoint + musebaq + rumination:Timepoint + (1 | id), data = s1longExplore)

tab_model(selected)

plot_model(selected)
```
