---
title: "Study One: Confirmatory Data Analysis"
author: "Joel Larwood"
date: "2019-09-23"
output:
  workflowr::wflow_html:
    code_folding: hide
editor_options:
  chunk_output_type: console
---

# Pre-registration 

```{r processdata, message = FALSE, results = "hide", warning = FALSE}
library(tidyverse)
library(papaja)

s1raw <- read_csv("data/s1.csv")

names(s1raw)


s1 <- s1raw %>% 
  mutate(rrq_6 = 6 - rrq_6,
         rrq_9 = 6 - rrq_9,
         rrq_10 = 6 - rrq_10,
         musebaq = rowSums(dplyr::select(., musebaq_1:musebaq_9)),
         Baseline = rowSums(dplyr::select(., deq_1_1:deq_1_4)),
         PostInduction = rowSums(dplyr::select(., deq_2_1: deq_2_4)),
         PostListening = rowSums(dplyr::select(., deq_3_1: deq_3_4)), 
         dif = PostListening - PostInduction
         ) 


s1 <- s1 %>% 
  mutate(rumination = rowMeans(dplyr::select(., rrq_1:rrq_12), na.rm = FALSE))

s1 %>% 
  dplyr::select(Baseline,
                PostInduction,
                PostListening,
                rumination,
                musebaq,
                hours.listen,
                reg.use_1,
                age) %>% 
  psych::describe()

write_csv(s1, "data/s1Processed.csv")

# s1 %>% var_labels(mecscale_1 = "brainstem",
#                         mecscale_2 = "Entrainment",
#                         mecscale_3 = "Memory", 
#                         mecscale_4 = "Conditioning",
#                         mecscale_5 = "Imagery",
#                         mecscale_6 = "Contagion", 
#                         mecscale_7 = "Expectancy",
#                         mecscale_8 = "Appraisal", 
#                   reg.use_1 = "Regulatory Use Probability")
```

# Reliabilities 

```{r s1alphas, echo = FALSE}

baseline <- psych::alpha(dplyr::select(s1, deq_1_1:deq_1_4))$total$raw_alpha
postinduction <- psych::alpha(dplyr::select(s1, deq_2_1:deq_2_4))$total$raw_alpha
postlistening <- psych::alpha(dplyr::select(s1, deq_3_1:deq_3_4))$total$raw_alpha
rumalpha <- psych::alpha(dplyr::select(s1, rrq_1:rrq_12))$total$raw_alpha
musebaqalpha<- psych::alpha(dplyr::select(s1, musebaq_1:musebaq_9))$total$raw_alpha

```

The alpha for the DEQ - Sadness at Baseline was `r baseline`

The alpha for the DEQ DEQ - Sadness at Post Induction  was `r postinduction`

The alpha for the DEQ _ Sadness at post Listening was `r postlistening`

The alpha for rumination scores was `r rumalpha`

The alpha for the cognitive and emotion regulation scale of the MUSEBAQ was `r musebaqalpha`


# Manipulation Check

```{r manipulationcheck, results = 'hide'}
s1Manipulation <- t.test(s1$PostInduction, s1$Baseline, paired = TRUE) 

apa::t_apa(s1Manipulation)
apa::t_apa(s1Manipulation, format = "rmarkdown")

```
The manipulation/induction of sadness was succesful, `r apa_print(t.test(s1$PostInduction, s1$Baseline, paired = TRUE))$full_result *t*(381)` = 14.01, *p* < .001, *d* = 0.72, with scores rising from baseline (*M* `r printnum(mean(s1$Baseline))`, *SD* = `r printnum(sd(s1$Baseline))` to Post induction (*M* = `r printnum(mean(s1$PostInduction))`, *SD* = `r printnum(sd(s1$PostInduction))`)

# Hypothesis Test 

A significant interaction was found. 
```{r message = FALSE}

library(sjlabelled)
s1long <- s1 %>% 
  gather(key = Timepoint,
         value = Sadness,
         factor_key = TRUE,
         PostInduction, PostListening) 

write_csv(s1long, "data/s1long.csv")
  

library(lmerTest)
library(sjPlot)

s1glmm <- lmerTest::lmer(Sadness~1 + Timepoint + rumination + Timepoint:rumination + (1 |id), data = s1long)

s1ancova <- afex::aov_ez(id = "id",
                         dv = "Sadness", 
                         within = "Timepoint", 
                         covariates = "rumination", 
                         data = s1long)
tab_model(s1glmm)
```

Here a main effect of timepoint was found `r apa_print(s1ancova)$full_result$Timepoint ` withs scores increasing from post induction (*M* `r printnum(mean(s1$PostInduction))`, *SD* = `r printnum(sd(s1$PostInduction))`) to post listening (*M* `r printnum(mean(s1$PostListening))`, *SD* = `r printnum(sd(s1$PostListening))`). This increase was qualified by an interaction with rumination, `r apa_print(s1ancova)$full_result$Timepoint:rumination`, such that greater increases in sadness were seen in participants higher in rumination. 


This interaction showed a larger increase in sadness for people higher in rumination 
```{r s1hypothesisplot}

library(sjPlot)

sjPlot::plot_model(s1glmm,
                   type = "int",
                   mdrt.values = "meansd",
                   ci.level = NULL,
                   legend.title = "Rumination\n (- 1SD, Mean, + 1 SD)",
                   show.values = TRUE,
                   show.p = TRUE,
                   order.terms = c(1,2,3)
                   ) + 
  ggplot2::theme(title = element_blank())+ 
  ggpubr::theme_pubr(legend = "right")
```

The simple effects showed that sadness increased for all levels of rumunation 
```{r simpleslopes}

minusrum <- mean(s1$rumination, na.rm = TRUE)-sd(s1$rumination, na.rm = TRUE)
plusrum <- mean(s1$rumination, na.rm = TRUE)+sd(s1$rumination, na.rm = TRUE)
meanrum <- mean(s1$rumination, na.rm = TRUE)


s1SimpleList <- list(rumination = c(minusrum, plusrum, meanrum), Timepoint = c("PostInduction", "PostListening"))

s1SimpleSlopes <- emmeans::emmeans(s1glmm, ~rumination*Timepoint, at = s1SimpleList)

emmeans::contrast(s1SimpleSlopes, "pairwise", by = "rumination")
```

