---
title: "StudtOneClusterExplore"
author: "Joel Larwood"
date: "2019-10-04"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## Import cluter variables

```{r s1MusicClusterExploreLoadIn}
library(tidyverse) 
s1clusters <- read_csv("data/s1clusters.csv") %>% 
  mutate(spotifycluster = if_else(KmeansCluster == 1, 
                                  "Postive Valence/High Energy", 
                                    if_else(KmeansCluster == 2, 
                                            "Negative Valence/Low Energy", 
                                            "Negative Valence/High Energy")), 
         spotifycluster = as_factor(spotifycluster))

```

# Plot clusters 
```{r plotcluster}
library(ggpubr)
ggpubr::ggscatter(s1clusters, 
                  x = "valence", 
                  y = "energy", 
                  color = "spotifycluster",
                  star.plot = TRUE,
                  palette = "simpsons",
                  legend = "right",
                  legend.title = "Cluster",
                  xlab = "Spotify valence metric",
                  ylab = "Spotify energy metric", 
                  ggtheme = theme_pubr(base_family = "Times New Roman")) +
  scale_y_continuous(breaks = c(0, .25, .5, .75, 1)) +
  scale_x_continuous(breaks =c(0, .25, .5, .75, 1)
                     )

```

# Describe clusters 

## Number in cluster 
```{r CompareS1ClusterN}
library(RVAideMemoire)

s1clusterN <- count(s1clusters, spotifycluster)  
chisq.test(s1clusterN$n)
chisq.multcomp(s1clusterN$n)

ggpubr::ggbarplot(data = s1clusterN, 
                  x = "spotifycluster",
                  color = "spotifycluster", 
                  fill = "spotifycluster", 
                  legend = "none",
                  y = "n", 
                  palette = "simpsons", 
                  ylab = "Participants per cluster", 
                  xlab = "Spotify cluster") 
                     
```


```{r clustercomparison}

MechPropSummary <- s1clusters %>% 
    drop_na(spotifycluster) %>% 
  group_by(spotifycluster) %>% 
  summarize(Brainstem=sum(brainstem=="Yes", na.rm = TRUE)/n(),
            Entrainment = sum(Entrainment=="Yes", na.rm = TRUE)/n(),
            Memory = sum(Memory=="Yes", na.rm = TRUE)/n(),
            Conditioning = sum(Conditioning == "Yes", na.rm = TRUE)/n(),
            Imagery = sum(Imagery == "Yes", na.rm = TRUE)/n(),
            Contagion = sum(Contagion == "Yes", na.rm = TRUE)/n(),
            Expectancy = sum(Expectancy == "Yes", na.rm = TRUE)/n(),
            Appraisal = sum(Appraisal == "Yes", na.rm = TRUE)/n() 
  ) 

SpreadContingencys1 <- MechPropSummary %>% 
  mutate(cluster = spotifycluster) %>% 
  gather(key = spotifycluster, 
         value = proportion, 
        Brainstem:Appraisal) %>% 
  mutate(Mechanism = spotifycluster)
library(tableone)

tableone::CreateCatTable(vars = c("brainstem"  ,  
                                  "Entrainment"  ,
                                  "Memory"     ,   
                                  "Conditioning"  ,
                                  "Imagery"  ,
                                  "Contagion"    , 
                                  "Expectancy"   , 
                                  "Appraisal"), 
                         strata = "KmeansCluster", 
                         data = s1clusters)


fisher.multcomp(xtabs(~Entrainment + KmeansCluster, data = s1clusters))$p.value
fisher.multcomp(xtabs(~Memory + KmeansCluster, data = s1clusters))$p.value
fisher.multcomp(xtabs(~Conditioning + KmeansCluster, data = s1clusters))$p.value
fisher.multcomp(xtabs(~Contagion + KmeansCluster, data = s1clusters))$p.value
fisher.multcomp(xtabs(~Appraisal + KmeansCluster, data = s1clusters))$p.value

ggpubr::ggbarplot(data = SpreadContingencys1, 
                  x = "Mechanism", 
                  y = "proportion", 
                  color = "cluster", 
                  fill = "cluster", 
                  position = position_dodge(0.9), 
                  palette = "simpsons",
                  legend = "top", 
                  xtickslab.rt = 45, 
                  ggtheme = theme_pubr(base_family = "Times New Roman")) +
ggplot2::scale_y_continuous(breaks=c(0, .2,.4,.6,.8,1)) + 
  ggplot2::ylim(0, 1) +
  ggplot2::ylab("Proportion of yes response")

```


## Rumination
```{r S1ClusterCompareRum}
ggpubr::ggviolin(drop_na(s1clusters), 
                  x = "spotifycluster",
                  y = "rumination", 
                  fill ="spotifycluster",
                  palette = "simpsons",
                  legend = "none", 
                 add = "boxplot", 
                  xtickslab.rt = 35, 
                 ) + 
  ggplot2::scale_y_continuous(breaks = c(1,2,3,4,5))

library(afex)
apa::anova_apa(afex::aov_ez(id = "id", 
             dv = "rumination", 
             data = s1clusters, 
             between = "spotifycluster", 
             #covariate = "musebaq", 
             type = 3), 
             es = "ges"
             )

```

##MUSEBAQ 

```{r S1ClusterCompareMuse}
ggpubr::ggviolin(drop_na(s1clusters), 
                  x = "spotifycluster",
                  y = "musebaq", 
                  fill ="spotifycluster",
                  palette = "simpsons",
                  legend = "none", 
                 add = "boxplot", 
                 xtickslab.rt = 35 
                 ) 

apa::anova_apa(afex::aov_ez(id = "id", 
             dv = "musebaq", 
             data = s1clusters, 
             between = "spotifycluster", 
             type = 3), 
             es = "ges"
             )
```

##Likely regulation use 
```{r S1ClusterCompareUse}
ggpubr::ggviolin(drop_na(s1clusters), 
                  x = "spotifycluster",
                  y = "reg.use_1", 
                  fill ="spotifycluster",
                  palette = "simpsons",
                  legend = "none", 
                 add = "boxplot",            
                 xtickslab.rt = 35, 
                 ) 

kruskal.test(reg.use_1 ~ spotifycluster, data = s1clusters)

```

## Clusters and Sadness changes 
How do the three different clusters predict sadness 

```{r S1ClustetrTimepointModel}
s1ClusterLong <- s1clusters %>% 
  gather(key = Timepoint, 
         value = Sadness, 
         PostInduction,PostListening)

library(lmerTest)
library(sjPlot)

s1ClusterSadness <- lmerTest::lmer(Sadness~1+Timepoint*spotifycluster + (1 |id), data = s1ClusterLong)
tab_model(s1ClusterSadness)
anova(s1ClusterSadness)
plot_model(s1ClusterSadness, 
           type = "int")

emmeans::contrast(emmeans::emmeans(s1ClusterSadness, ~Timepoint*spotifycluster), "pairwise", by = "spotifycluster")
```

# Looking at lyric information 

## Data organisation
I need to create a tibble with unique artist and song names. 
Some songs appear multiple times so I want to make sure I only have each song once for when I `group_by` for sentimment later
```{r S1lyricPullPrep}
library(genius)

TrackTibbleS1 <- s1clusters %>% 
  distinct(track_uri, .keep_all = TRUE) %>% 
  select(track_name, artist_name, spotifycluster, track_uri)

```

This script pulls the lyrics on a ine by line basis for all songs that can be found on [Genius](http://genius.com)
```{r PullS1lyrics, cahce = TRUE}
S1Lyrics <- TrackTibbleS1 %>% 
  genius::add_genius(artist = artist_name, 
                     title = track_name, 
                     type = "lyrics") %>% 
  unite(track_artist, 
        track_name, artist_name, 
        sep = "_", 
        remove = FALSE) %>% 
  drop_na(lyric)

dplyr::n_distinct(S1Lyrics$track_artist)
```

The script found `r print(dplyr::n_distinct(S1Lyrics$track_artist))` tracks out of the `r print (dplyr::n_distinct(TrackTibbleS1$track_uri))`

Now that I have the lyrics I need to put them into a [tidytext](https://www.tidytextmining.com/tidytext.html) fromat where there is a single word for every row. From this I can group by the song and calculate a sentiment. 
```{r UnnestS1Lyrics}
library(tidytext)
S1LyricsUnnest <- S1Lyric %>% 
  tidytext::unnest_tokens(word, lyric)
```

