---
title: "Study Two: Exploratorty Data Analysis"
author: "Joel Larwood"
date: "2019-09-23"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

# An exploratory saturdated model

In the dataset we also collected data about the BRECVEMA mechanism occuring during listening, demogrpahics and how likely they were to use the song for regulation. 

```{r loadS2data, message = FALSE}
library(tidyverse)
s2longExplore <- read_csv("data/s2long.csv") %>% 
  dplyr::select(id, 
                Sadness,
                Timepoint, 
                rumination, 
                Baseline,
                age,
                gender, 
                contains("mec"), 
                musebaq, 
                reg.use_1, 
                valence, 
                energy) %>% 
  drop_na()  %>% 
   mutate_at(.vars = vars(mecscale_1:mecscale_8), 
              factor) %>% 
   mutate_at(.vars = vars (mecscale_1:mecscale_8),
             .funs = forcats::fct_recode, 
             "No" = "2", 
             "Yes" = "1") %>% 
    dplyr::rename(brainstem = mecscale_1,
                        Entrainment = mecscale_2,
                        Memory = mecscale_3, 
                        Conditioning = mecscale_4,
                        Imagery = mecscale_5, 
                        Contagion = mecscale_6, 
                        Expectancy = mecscale_7,
                        Appraisal = mecscale_8)
```

So I want to build some models with control mechanisms coming in at each point 

Model 1 is the timepoint only model 
```{r timepointonly, message=FALSE}
library(sjPlot)
timepoint <- lmerTest::lmer(Sadness~1 + Timepoint + (1 |id), data = s2longExplore)
tab_model(timepoint)

```

Model 2 I add demographics 

```{r message=FALSE}
demo <- lmerTest::lmer(Sadness~1 + Timepoint + age + gender + (1 |id), data = s2longExplore)
tab_model(demo)
```
 Model 3 I add spotify data 
 
```{r message=FALSE}
spotifyvar <- lmerTest::lmer(Sadness~1 + Timepoint + age + gender + valence + energy +  (1 |id), data = s2longExplore)
tab_model(spotifyvar)
```

model 4 I add the brecvema mechanisms 
```{r message=FALSE}
mecscale <- lmerTest::lmer(Sadness~1 + Timepoint + age + gender + valence + energy + brainstem + Entrainment + Memory + Conditioning + Imagery + Contagion + Expectancy + Appraisal + (1 |id), data = s2longExplore)

tab_model(mecscale)
```

model 5 I add how likely they are to listen to the song when they are sad  
```{r message=FALSE}
likelyuse <- lmerTest::lmer(Sadness~1 + Timepoint + age + gender + valence + energy + brainstem + Entrainment + Memory + Conditioning + Imagery + Contagion + Expectancy + Appraisal + reg.use_1 + (1 |id), data = s2longExplore)

tab_model (likelyuse)
```
model 6 I add the MUSEBAQ 

```{r message=FALSE}
musebaqglmm <- lmerTest::lmer(Sadness~1 + Timepoint + age + gender + valence + energy + brainstem + Entrainment + Memory + Conditioning + Imagery + Contagion + Expectancy + Appraisal+ reg.use_1 + musebaq + (1 |id), data = s2longExplore)

tab_model(musebaqglmm)
```

model 7 I add rumiation 
```{r message=FALSE}
ruminationmain <- lmerTest::lmer(Sadness~1 + Timepoint + age + gender + valence + energy + brainstem + Entrainment + Memory + Conditioning + Imagery + Contagion + Expectancy + Appraisal+ reg.use_1 + musebaq + rumination +  (1 |id), data = s2longExplore)

tab_model(ruminationmain)
```

Finally I add the interaction term 
```{r message=FALSE}
ruminationint <- lmerTest::lmer(Sadness~1 + Timepoint + age + gender + valence + energy + brainstem + Entrainment + Memory + Conditioning + Imagery + Contagion + Expectancy + Appraisal + reg.use_1 + musebaq +rumination + rumination:Timepoint + (1 |id), data = s2longExplore)

tab_model(ruminationint)
```
## Model comparisons 

Now I want to compare these models 
```{r message=FALSE}
knitr::kable(anova(timepoint, demo, spotifyvar, mecscale, likelyuse, musebaqglmm, ruminationmain, ruminationint))
```

# Automatic Model 

Now I am going to do an exploratory analysis to find the best fitting model

```{r message = FALSE}
library(buildmer)
saturatedformula <- Sadness~1 + Timepoint + age + gender + valence + energy + brainstem + Entrainment + Memory + Conditioning + Imagery + Contagion + Expectancy + Appraisal + reg.use_1 + musebaq +rumination + rumination:Timepoint + (1 |id)

buildmer::buildmer(formula = saturatedformula, data = s2longExplore, crit = "AIC")

```


the best model was identifed as 


```{r, message=FALSE}
selected <- lmerTest::lmer(Sadness ~ 1 + rumination + reg.use_1 + brainstem + Appraisal + Timepoint + musebaq + rumination:Timepoint + (1 | id), data = s2longExplore)
```

It returns this 
```{r, message=FALSE}
tab_model(selected)

plot_model(selected)
```
    
# Exploring correaltions with rumination 

```{r rumcor, message = FALSE}

s2explore <- read_csv("data/s2Processed.csv") %>% 
  mutate(rumsplit = if_else(.$rumination < median(rumination, na.rm = TRUE), 
                            "Low", "High"))
```


```{r s2spotify, message = FALSE, warning = FALSE}

library(ggsci)

# s2explore %>% 
#   ggplot2::ggplot(aes(x = valence,
#                       y = energy,
#                       fill = rumination, 
#                       color = rumination)) +
#   geom_point(size = 5, alpha = .5) +
#   geom_hline(yintercept = .5) +
#   geom_vline(xintercept =.5) +
#   ylim(0,1) +
#   xlim(0,1) +
#   ggplot2::geom_point(aes(fill = rumination)) +
#   ggplot2::geom_hline(yintercept = .5) +
#   ggplot2::geom_vline(xintercept =.5) + 
#   ggplot2::ylim(0,1) + 
#   ggplot2::xlim(0,1) +
#   ggpubr::stat_cor(label.x = .75, 
#                    label.y = .95) + 
#   ggpubr::theme_pubr(legend = "right") +
#   ggplot2::stat_smooth(method = "lm")


ggpubr::ggscatterhist(s2explore,
                      x = "valence",
                      y = "energy",
                      palette = "simpsons",
                      color = "rumsplit",
                      fill = "rumsplit",
                      size = 3,
                      legend = "right",
                      xlab = "Spotify valence metric",
                      ylab = "Spotify energy metric",
                      conf.int = TRUE,
                      margin.params = list(fill = "rumsplit"),
                      legend.title = "Rumination \nScore",
                      xlim = c(0, 1),
                      ylim = c(0, 1),
                      mean.point = TRUE) 

```



