---
title: "SStudy Two: Exploratorty Data Analysis"
author: "Joel Larwood"
date: "2019-09-23"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

# An exploratory saturdated model

In the dataset we also collected data about the BRECVEMA mechanism occuring during listening, demogrpahics and how likely they were to use the song for regulation. 

```{r loadS2data}
library(tidyverse)
s2longExplore <- read_csv("data/s2long.csv") %>% 
  dplyr::select(id, 
                Sadness,
                Timepoint, 
                rumination, 
                Baseline,
                age,
                gender, 
                contains("mec"), 
                musebaq, 
                reg.use_1, 
                valence, 
                energy) %>% 
  drop_na()  %>% 
   mutate_at(.vars = vars(mecscale_1:mecscale_8), 
              factor) %>% 
   mutate_at(.vars = vars (mecscale_1:mecscale_8),
             .funs = forcats::fct_recode, 
             "Yes" = "1", 
             "No" = "2")
```

In this data set there are `length(unique(s2longExplore$id))` participants 

To find the best model I am going to saturdate a GLMM with all variables and the interaction between time and rumination. To do this I will be looking at the conditional AIC and use a backward stepwise approach from the maximal model 

```{r}
s2max <- lmerTest::lmer(Sadness~1 + Timepoint + age + gender + valence + energy + mecscale_1 + mecscale_2 + mecscale_3 + mecscale_4 + mecscale_5 + mecscale_6 + mecscale_7 + mecscale_8 + reg.use_1 + musebaq +rumination + rumination:Timepoint + (1 |id), data = s2longExplore)
```

```{r}

# step(s2max, alpha.fixed = .1)
# 
# tab_model(get_model(step(s2max, alpha.fixed = .1)))
# 
# plot_model(get_model(step(s2max, alpha.fixed = .1)))
```

So I want to build some models with control mechanisms coming in at each point 

Model 1 is the timepoint only model 
```{r timepointonly}
library(sjPlot)
timepoint <- lmerTest::lmer(Sadness~1 + Timepoint + (1 |id), data = drop_na(s2long))
tab_model(timepoint)

```

Model 2 I add demographics 

```{r}
demo <- lmerTest::lmer(Sadness~1 + Timepoint + age + gender + (1 |id), data = drop_na(s2long))
tab_model(demo)
```
 Model 3 I add spotify data 
 
```{r}
spotifyvar <- lmerTest::lmer(Sadness~1 + Timepoint + age + gender + valence + energy +  (1 |id), data = drop_na(s2long))
tab_model(spotifyvar)
```

model 4 I add the brecvema mechanisms 
```{r}
mecscale <- lmerTest::lmer(Sadness~1 + Timepoint + age + gender + valence + energy + mecscale_1 + mecscale_2 + mecscale_3 + mecscale_4 + mecscale_5 + mecscale_6 + mecscale_7 + mecscale_8 + (1 |id), data = drop_na(s2long))

tab_model(mecscale)
```

model 5 I add how likely they are to listen to the song when they are sad  
```{r}
likelyuse <- lmerTest::lmer(Sadness~1 + Timepoint + age + gender + valence + energy + mecscale_1 + mecscale_2 + mecscale_3 + mecscale_4 + mecscale_5 + mecscale_6 + mecscale_7 + mecscale_8 + reg.use_1 + (1 |id), data = drop_na(s2long))

tab_model (likelyuse)
```
model 6 I add the MUSEBAQ 

```{r}
musebaqglmm <- lmerTest::lmer(Sadness~1 + Timepoint + age + gender + valence + energy + mecscale_1 + mecscale_2 + mecscale_3 + mecscale_4 + mecscale_5 + mecscale_6 + mecscale_7 + mecscale_8 + reg.use_1 + musebaq + (1 |id), data = drop_na(s2long))

tab_model(musebaqglmm)
```

model 7 I add rumiation 
```{r}
ruminationmain <- lmerTest::lmer(Sadness~1 + Timepoint + age + gender + valence + energy + mecscale_1 + mecscale_2 + mecscale_3 + mecscale_4 + mecscale_5 + mecscale_6 + mecscale_7 + mecscale_8 + reg.use_1 + musebaq + rumination +  (1 |id), data = drop_na(s2long))

tab_model(rumination)
```

Finally I add the interaction term 
```{r}
ruminationint <- lmerTest::lmer(Sadness~1 + Timepoint + age + gender + valence + energy + mecscale_1 + mecscale_2 + mecscale_3 + mecscale_4 + mecscale_5 + mecscale_6 + mecscale_7 + mecscale_8 + reg.use_1 + musebaq +rumination + rumination:Timepoint + (1 |id), data = drop_na(s2long))

tab_model(ruminationint)
```

Now I want to compare these models 
```{r}
anova(timepoint, demo, spotifyvar, mecscale, likelyuse, musebaqglmm, ruminationmain, ruminationint)


```

Now I am going to do an exploratory backwards stepwise. This indicated that the best fitting model was the hypothesised model 

```{r}
lmerTest::step(S2glmm)
```

# Exploring correaltions with rumination 

```{r rumcor}

s2 <- read_csv("data/s2.csv") %>% 
  dplyr::select(rumination, 
                contains(mecscale))
```

